Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-02-24 manuscripts/TCS2022/tcs2022.tex
using plots instead of tables

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.9}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & - & - & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $1000^+$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & - & - & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & - & - & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & - & - & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $1000^+$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & - & - & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & - & - & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & - & - & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

Table~\ref{tab:pyboolnet_repo} shows the experimental results on the models from the official \texttt{PyBoolNet} repository\footnote{\url{https://github.com/hklarner/pyboolnet/tree/master/pyboolnet/repository}}.
Column \(n\) denotes the number of nodes of each model.
Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds, asking only for the first 1000 trap spaces.
In the case of \texttt{bioLQM}, ``N/A'' means that the number of all minimal trap spaces of the model is larger than 1000 and we did not recorded the running time of \texttt{bioLQM} because it always requires to compute all minimal trap spaces.
A number in bold indicates a ratio greater than three compared to the best result.
``NM'' indicates a non-locally-monotonic model.
There are four variants of \texttt{Trappist}: SAT (i.e., the MaxSAT-based method shown in Subsection~\ref{subsec:computation_csp}), CP (i.e., the CP-based method shown in Subsection~\ref{subsec:computation_csp}), ILP (i.e., the ILP-based method shown in Subsection~\ref{subsec:computation_ilp}), and ASP (i.e., the ASP-based method shown in Subsection~\ref{subsec:computation_asp}).

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.8}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & LQM & PBN & \texttt{mpbn} & SAT & CP & ILP & ASP \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & - & - & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & - & - & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & - & - & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & - & - & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & - & - & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & - & - & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & - & - & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & - & - & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & - & - & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $1000^+$ & N/A & 0.11 & 0.36 & 0.17 & - & - & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & - & - & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & - & - & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $1000^+$ & N/A & \textbf{DNF} & 0.50 & 0.34 & - & - & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & - & - & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & - & - & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $1000^+$ & N/A & 0.09 & 0.55 & 0.37 & - & - & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $1000^+$ & N/A & \textbf{107.57} & 0.76 & 0.56 & - & - & 0.16 \\

@@

\begin{table}[!htb]
  \caption{Results on N-K models.}
  \centering%
  \label{tab:result_N_K}
  \begin{tabular}{rrrrrrrr}
    \toprule
    & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){5-8}
    \(n\) & \texttt{LQM} & \texttt{mpbn} & \texttt{PBN} & SAT & CP & ILP & ASP \\
    \midrule
    100 & 50 ($>$ 180) & 50 (N/A) & 0 (0.07) & 0 (0.05) & - () & - () & 0 (0.09) \\
    150 & 50 ($>$ 180) & 50 (N/A) & 0 (0.14) & 0 (0.10) & - () & - () & 0 (0.14) \\
    200 & 50 ($>$ 180) & 50 (N/A) & 0 (0.43) & 0 (0.25) & - () & - () & 0 (0.24) \\
    250 & 50 ($>$ 180) & 50 (N/A) & 0 (1.92) & 0 (1.04) & - () & - () & 0 (0.56) \\
    300 & 50 ($>$ 180) & 50 (N/A) & 0 (9.68) & 0 (4.46) & - () & - () & 0 (1.83) \\
    350 & 50 ($>$ 180) & 50 (N/A) & 1 (46.54) & 0 (20.09) & - () & - () & 0 (6.10) \\
    400 & 50 ($>$ 180) & 50 (N/A) & 29 (144.09) & 12 (90.36) & - () & - () & 1 (33.01) \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\usepackage{pgfplots}
\pgfplotsset{width=10cm,compat=1.13}

@@

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.9}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & - & - & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $1000^+$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & - & - & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & - & - & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & - & - & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $1000^+$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & - & - & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & - & - & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & - & - & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

Table~\ref{tab:pyboolnet_repo} shows the experimental results on the models from the official \texttt{PyBoolNet} repository\footnote{\url{https://github.com/hklarner/pyboolnet/tree/master/pyboolnet/repository}}.
Column \(n\) denotes the number of nodes of each model.
Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds, asking only for the first 1000 trap spaces.
In the case of \texttt{bioLQM}, ``N/A'' means that the number of all minimal trap spaces of the model is larger than 1000 and we did not recorded the running time of \texttt{bioLQM} because it always requires to compute all minimal trap spaces.
A number in bold indicates a ratio greater than three compared to the best result.
``NM'' indicates a non-locally-monotonic model.
There are four variants of \texttt{Trappist}: \texttt{SAT} (i.e., the MaxSAT-based method shown in Subsection~\ref{subsec:computation_csp}), \texttt{CP} (i.e., the CP-based method shown in Subsection~\ref{subsec:computation_csp}), \texttt{ILP} (i.e., the ILP-based method shown in Subsection~\ref{subsec:computation_ilp}), and \texttt{ASP} (i.e., the ASP-based method shown in Subsection~\ref{subsec:computation_asp}).

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.82}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & - & - & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & - & - & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & - & - & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & - & - & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & - & - & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & - & - & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & - & - & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & - & - & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & - & - & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $1000^+$ & N/A & 0.11 & 0.36 & 0.17 & - & - & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & - & - & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & - & - & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $1000^+$ & N/A & \textbf{DNF} & 0.50 & 0.34 & - & - & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & - & - & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & - & - & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $1000^+$ & N/A & 0.09 & 0.55 & 0.37 & - & - & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $1000^+$ & N/A & \textbf{107.57} & 0.76 & 0.56 & - & - & 0.16 \\

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
	\begin{semilogxaxis}[
		%title={},
		xlabel={Time (s)},
		ylabel={Models solved},
		xmin=-1, xmax=180,
		log basis x={10},
		%scale only axis,
		ymin=0, ymax=350,
		%ymode=log,
		%log basis y={10},
		xtick={0.5, 1, 2, 5, 10, 20, 50, 100, 180},
		xticklabels = {0.5, 1, 2, 5, 10, 20, 50, 100, 180},
		ytick={0, 50, 100, 150, 200, 250, 300, 350},
		y=0.5cm/30,
		%legend style={font=\fontsize{7}{8}\selectfont},
		%legend style={at={(0.0,-0.1)},anchor=north},
		legend pos=outer north east,
		ymajorgrids=true,
		grid style=dashed,
	]

	\addplot[
		smooth,
		thick,
		color=blue,
		mark=*,
	]
	coordinates {
		(0.5, 141)(1, 174)(2, 193)(5, 220)(10, 247)(20, 262)(50, 285)(100, 306)(180, 320)
	}; \addlegendentry{\texttt{PyBoolNet}}

	\addplot[
		smooth,
		thick,
		%dashed,
		color=cyan,
		mark=triangle,
	]
	coordinates {
		(0.5, 0)(1, 0)(2, 0)(5, 0)(10, 0)(20, 0)(50, 0)(100, 0)(180, 0)
	}; \addlegendentry{\texttt{mpbn}}

	\addplot[
		smooth,
		thick,
		dashed,
		color=orange,
		mark=asterisk,
	]
	coordinates {
		(0.5, 0)(1, 0)(2, 0)(5, 0)(10, 0)(20, 0)(50, 0)(100, 0)(180, 0)
	}; \addlegendentry{\texttt{bioLQM}}

	\addplot[
		smooth,
		thick,
		%dashed,
		color=magenta,
		mark=square,
	]
	coordinates {
		(0.5, 164)(1, 190)(2, 214)(5, 249)(10, 266)(20, 291)(50, 317)(100, 328)(180, 338)
	}; \addlegendentry{\texttt{Trappist-maxSAT}}

	\addplot[
		smooth,
		thick,
		dashed,
		color=violet,
		mark=star,
	]
	coordinates {
		(0.5, 179)(1, 211)(2, 244)(5, 274)(10, 304)(20, 327)(50, 339)(100, 347)(180, 349)
	}; \addlegendentry{\texttt{Trappist-ASP}}

	\end{semilogxaxis}
	\end{tikzpicture}
	\caption{Cumulative numbers of random models solved by the competing methods with respect to enumerating the first 1000 minimal trap spaces.}
	\label{fig:random_cumul_first}
\end{figure}

%\begin{table}[!htb]
%  \caption{Results on N-K models.}
%  \centering%
%  \label{tab:result_N_K}
%  \begin{tabular}{rrrrrrrr}
%    \toprule
%    & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
%    \cmidrule(rr){5-8}
%    \(n\) & \texttt{LQM} & \texttt{mpbn} & \texttt{PBN} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
%    \midrule
%    100 & 50 ($>$ 180) & 50 (N/A) & 0 (0.07) & 0 (0.05) & - () & - () & 0 (0.09) \\
%    150 & 50 ($>$ 180) & 50 (N/A) & 0 (0.14) & 0 (0.10) & - () & - () & 0 (0.14) \\
%    200 & 50 ($>$ 180) & 50 (N/A) & 0 (0.43) & 0 (0.25) & - () & - () & 0 (0.24) \\
%    250 & 50 ($>$ 180) & 50 (N/A) & 0 (1.92) & 0 (1.04) & - () & - () & 0 (0.56) \\
%    300 & 50 ($>$ 180) & 50 (N/A) & 0 (9.68) & 0 (4.46) & - () & - () & 0 (1.83) \\
%    350 & 50 ($>$ 180) & 50 (N/A) & 1 (46.54) & 0 (20.09) & - () & - () & 0 (6.10) \\
%    400 & 50 ($>$ 180) & 50 (N/A) & 29 (144.09) & 12 (90.36) & - () & - () & 1 (33.01) \\
%    \bottomrule
%  \end{tabular}
%\end{table}
